---
title: "Lab 00 - Hello IDS!"
author: "Maisie Byrne"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Maisie", "Raven", "Julia", 
           "Elana"),
  github_username = c("maisiebyrne", "vendingmchne", "julia-toma", 
                      "elgoldie3"), 
  colour = c("cornflowerblue", "magenta", "powderblue", 
             "steelblue"),
  hobby = c("baking", "listening to music", "drawing", 
            "reading"),
  favourite_number = c(4, 5, 8, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The favourite number of different team members, in their favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "team member", 
          y = "favourite number",
          title = "DS class favourite numbers")
```

labs means labels

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Could split hobbies into categories e.g. sports, arts, academic related etc so that people's interests are represented by the chart more simply.
